### 2016-01-18 paper.tex
Remove 'TTL' and describe as digital signal edge

\paragraph{Synchronization.} The three data acquisition instrumentation
subsystems---motion controller, NI DAQ (performance measurements), and Vectrino+
(wake velocity measurements)---started sampling at precisely the same time each
tow, after being triggered by a TTL pulse created by the motion controller. This
strategy retained synchronization for all performance signal samples (tow speed,
torque, drag, angular velocity), ensuring precise calculation of, e.g., power
coefficient. Since there was also synchronization of the initial sample from
each of the three subsystems, correlation of events in the performance and wake
signals is also possible.

>>>>

\paragraph{Synchronization.} The three data acquisition instrumentation
subsystems---motion controller, NI DAQ (performance measurements), and Vectrino+
(wake velocity measurements)---started sampling at precisely the same time each
tow, after being triggered by a digital signal edge from the motion controller.
This strategy retained synchronization for all performance signal samples (tow
speed, torque, drag, angular velocity), ensuring precise calculation of, e.g.,
power coefficient. Since there was also synchronization of the initial sample
from each of the three subsystems, correlation of events in the performance and
wake signals is also possible.
